\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[left=1.5cm, right=1.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{tikz}
\newcommand{\given}{\,|\,}

\title{}
\author{}
\date{}

\begin{document}
\maketitle

%\abstract{}

% Need this after the abstract
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

Hybrid of FNC and SSA. Condition on the memory state but also, in the prior
information, assert that I will get {\em some} memory state, with a uniform
prior over conscious beings.

The hypothesis space under consideration is
\begin{align}
\overbrace{\{0, 1, 2, ...\}}^{N_*} \times
\overbrace{[0, 1]}^{\theta} \times
\overbrace{[0, 1]}^{\phi} \times
\overbrace{\{0, 1, 2, ...\}^{N_*}}^{\{n_i\}_{i=1}^{N_*}}.
\end{align}

For now assume $N^*$ is known.
The prior over the rest of the hypothesis space is
\begin{align}
p(\theta, \phi, \boldsymbol{n}) &\propto
    \frac{1}{\theta\phi}\prod_{i=1}^{N_*} p(n_i \given \theta, \phi).
\end{align}
For arguments' sake we will set the lower bounds on $\theta$ and $\phi$
to $\exp(-50)$.

Now, the probability distribution for the number of beings at each
star is some sort of zero-inflated distribution $f(n_i)$, with
where $f(0) = 1 - \theta\phi$ and we assume $f(n)$ has fixed shape
for $n \geq 1$ that does not depend on $\theta$ and $\phi$.

The probability that my memories exist (in this simple model) will be
proportional to the number of consciousnesses,
\begin{align}
P(\textnormal{Brendon exists} \given \theta, \phi, \boldsymbol{n})
    &= \epsilon\sum_{i=1}^{N_*} n_i.
\end{align}
This extends the space with the binary variable of my existence, so the
full joint is now
\begin{align}
p(\theta, \phi, \boldsymbol{n}, \textnormal{Brendon exists}) &\propto
    \left(\frac{1}{\theta\phi}\prod_{i=1}^{N_*} p(n_i \given \theta, \phi)\right)
    \left(\epsilon\sum_{i=1}^{N_*} n_i\right).
\end{align}

If we marginalise over $\boldsymbol{n}$, we get
\begin{align}
p(\theta, \phi, \textnormal{Brendon exists}) &\propto
    \frac{1}{\theta\phi}
    \sum_{n_1, ..., n_{N_*}}
    \left(\prod_{i=1}^{N_*} p(n_i \given \theta, \phi)\right)
    \left(\epsilon\sum_{i=1}^{N_*} n_i\right).
\end{align}
This looks ugly, but simplifies to the conditional expectation of the total
$\sum_i n_i$ given the parameters:
\begin{align}
p(\theta, \phi, \textnormal{Brendon exists}) &\propto
    \frac{1}{\theta\phi}
    \theta\phi E \epsilon,
\end{align}
where $E$ is the expectation of $n_i$ given that $n_i \geq 1$.
This is the strong FNC conclusion of abundant life.

However, if I take the data as something different --- I am going to get
{\em some} memories, so the space of possible datasets is not
$\{\textnormal{Brendon exists}, \textnormal{Brendon does not exist}\}$
but is instead the set of possible memories, there is an additional factor.
Instead we get 
\begin{align}
p(\theta, \phi, \boldsymbol{n}, \textnormal{Brendon exists},
  \textnormal{Brendon is returned}) &\propto
    \left(\frac{1}{\theta\phi}\prod_{i=1}^{N_*} p(n_i \given \theta, \phi)\right)
    \left\{
        \begin{array}{lr}
         \frac{\epsilon\sum_{i=1}^{N_*} n_i}{\sum_{i=1}^{N_*} n_i}, & \sum_i n_i \geq 1 \\
        0, & \textnormal{otherwise}
        \end{array}
    \right.\\
    &= \left(\frac{1}{\theta\phi}\prod_{i=1}^{N_*} p(n_i \given \theta, \phi)\right)
    \epsilon\mathds{1}\left(\sum_{i=1}^{N_*} n_i \geq 1\right).
\end{align}
Marginalising over $\boldsymbol{n}$ now gives
\begin{align}
p(\theta, \phi, \textnormal{Brendon exists},
  \textnormal{Brendon is returned}) &\propto
    \frac{1}{\theta\phi}
    \left(1 - (1 - \theta\phi)^{N_*}\right)
\epsilon.
\end{align}
I will call $\left(1 - (1 - \theta\phi)^{N_*}\right)\epsilon$ the full indexical
conditioning (FIC) likelihood.

\section{Australia and China}
Let $N_A$ be the population of Australia and let $N_C$ be the population of
China. Consider the joint probability distribution over these unknowns
and also my memories' existence and selection (both of which are binary
variables).
\begin{align}
p(N_A, N_C, \textnormal{existence}, \textnormal{selection})
    &= p(N_A, N_C)P(\textnormal{existence} \given N_A, N_C)
            P(\textnormal{selection} \given \textnormal{existence}, N_A, N_C)\\
    &= p(N_A, N_C)\left(\epsilon N_A\right)
            \left(\frac{1}{N_A + N_C}\right).
\end{align}
This gives exactly the SSA likelihood. Conversely, FNC gives $N_A\epsilon$
only.


\section{G and M Stars}
Suppose we now have separate parameters for $G$ and $M$ stars,
which are $\theta_G$, $\phi_G$, $\theta_M$, and $\phi_M$, and the numbers of
such stars are $N_G$ and $N_M$, with $N_* = N_G + N_M$.
Let BE=`Brendon exists', BR=`Brendon returned'.
Then we have
\begin{align}
p(\theta, \phi, \boldsymbol{n}, \textnormal{BE},
  \textnormal{BR}) &\propto
    p(\theta_G, \phi_G, \theta_M, \phi_M)
    \prod_{i=1}^{N_G} p(n_i \given \theta_G, \phi_G)
    \prod_{i=N_G+1}^{N_*} p(n_i \given \theta_M, \phi_M)
        P(\textnormal{BE} \given \boldsymbol{n})
                P(\textnormal{BR} \given \textnormal{BE})\\
    &=     p(\theta_G, \phi_G, \theta_M, \phi_M)
    \prod_{i=1}^{N_G} p(n_i \given \theta_G, \phi_G)
    \prod_{i=N_G+1}^{N_*} p(n_i \given \theta_M, \phi_M)
        \left(\epsilon\sum_{i=1}^{N_G}n_i\right) \\
    &\times
        \left\{
        \begin{array}{lr}
        \frac{1}{\sum_{i=1}^{N_*} n_i}, &\sum_{i=1}^{N_*} n_i \geq 1 \\
        0, &\textnormal{otherwise}.
        \end{array}
        \right.
\end{align}
Marginalising out $\boldsymbol{n}$, and assuming that the expected
number of observers around each G and M star that has observers
is a constant, gives
\begin{align}
p(\theta, \phi, \textnormal{BE},
  \textnormal{BR}) &\propto
    p(\theta_G, \phi_G, \theta_M, \phi_M)
    \left(1 - (1-\theta_G\phi_G)^{N_G}(1 - \theta_M\phi_M)^{N_M}\right)
    \frac{N_G\theta_G\phi_G}{N_G\theta_G\phi_G + N_M\theta_M\phi_M}.
\end{align}
which is a mild indication term for consciousness anywhere, multiplied
by an SSA term (Kipping style) for G vs M stars.


\section{13.8 Gyr}
Suppose conscious observers arise in the universe with probability distribution
$f(t)$ for the time $t$. We will just use SSA here, any indication term would
relate presumably to the normalisation of $f$.
The likelihood function is just $f(13.8)$. We can probably do some inference
analytically. Suppose $f(t)$ is a Gamma density
\begin{align}
f(t \given \alpha, \lambda) &= \frac{\lambda^{\alpha}}{\Gamma(\alpha)}
    t^{\alpha-1}\exp(-\lambda t).
\end{align}
Therefore the posterior will be given by
\begin{align}
p(\alpha, \lambda \given t) &\propto
    p(\alpha, \lambda)\frac{\lambda^{\alpha}}{\Gamma(\alpha)}
        13.8^{\alpha-1}\exp(-13.8\lambda).
\end{align}
Reading this, we can see that conditional on $\alpha$ the posterior over
$\lambda$ will itself be a Gamma density if we assign a flat or a log-uniform
prior over $\lambda$.


\end{document}

